Fitting phylogenetic generalized linear mixed-effect models using lme4

### 2017-10-30 ms.tex
pushing random text and updating parameters for single site simulation test
pushing draft looking THING

\section{Introduction}

Given a phylogenetic tree, phylogenetic models aim to find parsimonious methods that can be used to link ecological phenomena with the evolutionary processes that generate species and their traits. 
Ecologist have long considered the effects of functional traits and environmental conditions on pheotypic traits. 
For example, regression analyses of body temperature as a function of body size for animal within a clade, species compositions in different sites, etc.

@@

The standard problem of phylogenetic comparative methods is to analyze relationships among data where the observations are gathered from nodes (usually tips) of a phylogenetic tree.

@@

>>>>

\section{Introduction}
\ml{I will fill in appropriate citation later}

Given a phylogenetic tree, phylogenetic models aim to find parsimonious methods that can be used to link ecological phenomena with evolutionary processes that generate species and exhibit in their traits.
Ecologist have long considered the effects of species functional traits and environmental conditions on their phenotypic traits and also incorportating historical relationships of species.
Decades of work have created various different methods that enables researchers to analyze species relativeness problems/systems for different types of data and questions.
%For example, regression analyses of body temperature as a function of body size for animal within a clade, species compositions in different sites, etc. 
\ml{more examples...and reference}

The most widely used statistical method to model/fit related species data that accounts for phylogenetic structure is the phylogenetic regression (Felsenstein 1985). 
More recently, people use linear mixed model and generalized linear mixed model framework to model complex systems with phylogenetic structures.

Despite the choice of modeling strageties, there isn't a convient platform to do all and limited in model complexities additional complexities in the systems.

In this paper, we model it using lme4 and test it with simulated cases across platforms and fit it to dun (maybe more examples if we can find it) example.

We also compare different platforms.

@@

We generate test data using a simple glmm framework that varies in complexity in random effect.

\section{Phylogenetic Tree Transformation}
The standard problem of phylogenetic comparative methods is to analyze relationships among data where the observations are gathered from nodes (usually tips) of a phylogenetic tree.

@@

\subsection{Platforms}

...

\section{Results}

\section{Discussion}

\section{Conclusion}
